A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-03-19 paper/paper.tex
Removing confusing terminology \hat{Delta}

While ordinary semi-simplicial sets are presheaves over the semi-simplex category \DeltaHat, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus. There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.

>>>>

While ordinary semi-simplicial sets are presheaves over the semi-simplex category, augmented semi-simplicial sets are presheaves over, what we will define as, \DeltaPlus. There are different ways to define \DeltaPlus, up to equivalence, and we use a definition that will later straightforwardly extend to semi-cubical sets.

%% Notations
% simplicial, augmented, where
% Γ           Γ+         Augmented Simplicial Combinatorics through Category Theory
%                        José Manuel García-Calcines, María Teresa Rivas-Rodríguez, Luis Javier Hernández-Paricio, 2022

% semi-augmented, where
% ∆_s        HOMOLOGY IN RELATIVE SEMI-ABELIAN CATEGORIES, JULIA GOEDECKE, 2011

% simplicial, semi-simplicial, where
% Δ           Δ_inj            SEMI-SIMPLICIAL SPACES, JOHANNES EBERT AND OSCAR RANDAL-WILLIAMS, 2018
% Δ           Δ_inj            PhD, Josep Esquirol Esteve, 2019
% Δ           Δ'               Strict n-categories and augmented directed complexes model homotopy types, Andrea Gagna, 2018
% Δ           Δ_inj, Δ_{inj,aug} Ms Th. Jonas Dallend ̈orfer, 2019
